### 2023-11-07 Data/AnalysisData/codebook_Plot_26_data.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:38.16236"
output: github_document
---

@@

## Dataset description
The data contains 341 cases and 8 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.9.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:59:14.419679"
output: github_document
---

@@

## Dataset description
The data contains 1925 cases and 4 variables.

@@

```{r}
summaries <- read.csv("codebook_Plot_26_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H1.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:59:14.419679"
output: github_document
---

@@

## Dataset description
The data contains 1925 cases and 4 variables.

@@

```{r}
summaries <- read.csv("codebook_Plot_26_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:46.380662"
output: github_document
---

@@

## Dataset description
The data contains 154 cases and 91 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H1.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H2.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:46.380662"
output: github_document
---

@@

## Dataset description
The data contains 154 cases and 91 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H1.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:52:58.610667"
output: github_document
---

@@

## Dataset description
The data contains 154 cases and 90 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H2.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H3.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:52:58.610667"
output: github_document
---

@@

## Dataset description
The data contains 154 cases and 90 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H2.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:00:04.653618"
output: github_document
---

@@

## Dataset description
The data contains 713 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H3.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H4_avg.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:00:04.653618"
output: github_document
---

@@

## Dataset description
The data contains 713 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H3.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:47.475669"
output: github_document
---

@@

## Dataset description
The data contains 18 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H4_avg.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H4_multiple.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:47.475669"
output: github_document
---

@@

## Dataset description
The data contains 18 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H4_avg.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:41.005817"
output: github_document
---

@@

## Dataset description
The data contains 713 cases and 4 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H4_multiple.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H5.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:41.005817"
output: github_document
---

@@

## Dataset description
The data contains 713 cases and 4 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H4_multiple.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:56:39.032172"
output: github_document
---

@@

## Dataset description
The data contains 74 cases and 89 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H5.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H6.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:56:39.032172"
output: github_document
---

@@

## Dataset description
The data contains 74 cases and 89 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H5.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:47:39.749165"
output: github_document
---

@@

## Dataset description
The data contains 77 cases and 67 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H6.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_plot_256_data.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:47:39.749165"
output: github_document
---

@@

## Dataset description
The data contains 77 cases and 67 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H6.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:51.91642"
output: github_document
---

@@

## Dataset description
The data contains 924 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_256_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_plot_34_data_alpha.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:51.91642"
output: github_document
---

@@

## Dataset description
The data contains 924 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_256_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:49.637916"
output: github_document
---

@@

## Dataset description
The data contains 658 cases and 5 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_34_data_alpha.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_plot_34_data_omega.Rmd
added the final data preparation step, and the models for H1 and H3.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:49.637916"
output: github_document
---

@@

## Dataset description
The data contains 658 cases and 5 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_34_data_alpha.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:04:46.430554"
output: github_document
---

@@

## Dataset description
The data contains 558 cases and 5 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_34_data_omega.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
added the final data preparation step, and the models for H1 and H3.

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(psych)

@@

@@

```{r}

@@

# 1.9 is difficult, might be a scale as dv rather than voting behaviour.
```

@@

@@

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```
The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets. However, to the author's knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance. Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs. between variability. The formula used to calculate the ICC is presented below.

@@

A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.

>>>>

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(psych)
library(betareg)
library(lmerTest)
library(forcats)
library(GPArotation)

@@

# clearing up memory space by removing raw files from the environment
rm(coded_data_initial_raw, coded_data_revised_raw, coded_data_vignette_raw, 
   data_2.10.1, data_2.12, data_2.15, data_2.19.1, data_2.2, data_2.20, 
   data_2.23, data_2.3, data_2.4.1, data_2.4.2, data_2.8.2, data_3.5, data_5.1,
   data_5.4, data_5.5, data_5.7, data_5.9.1, data_ml1, data_ml3)

@@

@@

# 1.9 is difficult, might be a scale as dv rather than voting behavior.
```

@@

```{r Final Preparation of Data}
### this code prepares the various pieces of data to be ready to use for the analyses.
## confirmatory analyses
# for hypothesis 2
data_H2 <- data_prep_H2(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_H5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_H6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

# for hypothesis 1
data_H1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
# for hypothesis 3
data_H3 <- data_prep_H3(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
  data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
  data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, 
  data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.2_clean, data_3.8.2_clean, 
  data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
# for hypothesis 4
data_H4_multiple <- Data_prep_H4_multiple(data_H5, data_H3)
data_H4_avg <- Data_prep_H4_avg(data_H5, data_H4_multiple)

## graphs
# plot accompanying the results for Hypotheses 2, 5, & 6.
plot_256_data <- data_prep_plot_256(data_H6)
# plot accompanying the results for Hypotheses 2, & 6
Plot_26_data <- data_prep_plot_26(data_H6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
# plot accompanying the results for Hypotheses 3, & 4
plot_34_data_alpha <- data_prep_plot_34_alpha(data_H4_multiple)
plot_34_data_omega <- data_prep_plot_34_omega(data_H4_multiple)

### Exporting the final datasets for the analyses
# the open data
open_data(data = data_H2, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H2))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H2))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H2))), ".yml"))

open_data(data = data_H6, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H6))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H6))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H6))), ".yml"))

open_data(data = data_H5, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H5))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H5))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H5))), ".yml"))

open_data(data = data_H1, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H1))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H1))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H1))), ".yml"))

open_data(data = plot_256_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_256_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_256_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_256_data))), ".yml"))

open_data(data = Plot_26_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(Plot_26_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(Plot_26_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(Plot_26_data))), ".yml"))

open_data(data = data_H3, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H3))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H3))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H3))), ".yml"))

open_data(data = data_H4_multiple, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H4_multiple))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H4_multiple))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H4_multiple))), ".yml"))

open_data(data = data_H4_avg, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H4_avg))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H4_avg))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H4_avg))), ".yml"))

open_data(data = plot_34_data_alpha, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_34_data_alpha))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_34_data_alpha))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_34_data_alpha))), ".yml"))

open_data(data = plot_34_data_omega, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_34_data_omega))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_34_data_omega))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_34_data_omega))), ".yml"))

# clearing up memory space by removing intermediate files from the environment
rm(coded_data_original, coded_data_original_shortened, coded_data_replications)

@@

```{r Hypothesis 1 Model}
# first some descriptives of reliability reporting
# Measurement type per original and replication:
H1_descriptive_table_1 <- table(data_H1$rep_org, data_H1$N_items)

# amount of reliability reported per original and replication 
# (given that measure is a multiple item measure):
H1_descriptive_table_2 <- table(data_H1$rep_org[data_H1$N_items == "multiple item measure"], data_H1$reliability_type[data_H1$N_items == "multiple item measure"])

# New H1 test
# A chi square test for difference in N reliability reported for multiple 
# item measures.
H1_test_result <- chisq.test(data_H1$rep_org[data_H1$N_items == "multiple item measure"], data_H1$reliability_reported[data_H1$N_items == "multiple item measure"])

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```

```{r Hypothesis 3 Model}
# intercept only model to check the within and between group variance.
H3_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_H3))

# and same analyses for omega
# intercept only model to check the within and between group variance.
H3_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_H3[complete.cases(data_H3),]))

The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets. However, to the author's knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance. Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs. between variability. The formula used to calculate the ICC is presented below.

@@

A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 3.

```{r ICC calculations}
# alpha
# within group variance: 0.04384
# between group variance: 0.19824
ICC_alpha <- 0.19824 / (0.04384 + 0.19824)

# omega
# within group variance: 0.003779
# between group variance: 0.034025
ICC_omega <- 0.034025 / (0.003779 + 0.034025)
